Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-01-15 WSSSPE3/report/wg_appendix_eng_design.tex
Create wg_appendix_eng_design.tex
Former-commit-id: b358137b07892ef97a717f838b4d279978b4900d
Reformatted group members to itemized list to ensure they appear in the right place.
Former-commit-id: e4584de998d67127bdd327661163fca316f83c01
adding POC request to appendices
Former-commit-id: 42aa40a42eb82bf40df6e482de5fb48dc9085b8d
Update wg_appendix_eng_design.tex
Group members added.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Best Practices Group Discussion}
\label{sec:appendix_best_practices}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Group Members}
{\small
\begin{longtable}{ll}
   name            &  affiliation
\\ name2           &  affiliation2
\end{longtable}
}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Engineering Design Group Discussion}
\label{sec:appendix_eng_design}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo{add POC here}

\subsection{Group Members}

\begin{itemize}
\item Birgit Penzenstadler -- California State University, CA, USA
\item Colin C. Venters -- University of Huddersfield, Huddersfield, UK
\item Matthias Bussonnier -- UC Berkeley
\item Jeff McWhirter -- Geode Systems
\item Patrick Nichols -- National Center for Atmospheric Research
\item Ilian Todorov -- Science \& Technology Facilities Council, UK\\
\item Ian Taylor -- Cardiff University
\item Alexander Vyushkov -- University of Notre Dame

\end{itemize}
